\bf On Misuses of the Kolmogorov--Smirnov Test for One-Sample Goodness-of-Fit

### 2024-04-29 manuscript/manuscript.tex
add cover, minor typo fixes to ms and reply

\if1\blind
{
% Graduate level
The misuses of one-sample KS test can be easily incorporated into graduate level
classroom teaching for courses that cover parametric bootstrap. For example, at
the University of XX, YY has always included a demonstration of the misuse under 
unspecified parameters in STAT $\#\#\#\#$, XXXX. The
catalog description of this course includes: ``Use of computing for statistical
problems; obtaining features of distributions, fitting models and implementing
inference. Basic numerical methods, nonlinear statistical methods, numerical
integration, modern simulation methods.'' Bootstrap is covered under ``modern
simulation methods.''  The course is open to graduate students in Statistics,
others with permission. Detailed R code and graphical illustrations available in
the open-access course notes elucidate the distinctions between employing null
hypotheses with and without defined parameters (accessible at: 
\textit{author YY's github website}).
%\url{https://jun-yan.github.io/stat-5361/boot.html#parametric-bootstrap}).
Students were able to follow the demonstration closely, gaining a clear
understanding of the implications of using estimated parameters within test
statistics, and learning about the efficacy of the parametric bootstrap method
as a corrective measure.

@@

\section*{Data Availability Statement}
An R implementation of the proposed methods will be made publicly available upon 
publication.

>>>>

\if1\blind
{
% Graduate level
The misuses of one-sample KS test can be easily incorporated into graduate level
classroom teaching for courses that cover parametric bootstrap. For example, at
the University of XX, YY has always included a demonstration of the misuse under 
unspecified parameters in STAT $\#\#\#\#$, XXXX. The
catalog description of this course includes: ``Use of computing for statistical
problems; obtaining features of distributions, fitting models and implementing
inference. Basic numerical methods, nonlinear statistical methods, numerical
integration, modern simulation methods.'' Bootstrap is covered under ``modern
simulation methods.''  The course is open to graduate students in Statistics,
others with permission. Detailed R code and graphical illustrations available in
the open-access course notes elucidate the distinctions between employing null
hypotheses with and without defined parameters (accessible at: 
\textit{author YY's github website; material printed to pdf for blinded review}).
%\url{https://jun-yan.github.io/stat-5361/boot.html#parametric-bootstrap}).
Students were able to follow the demonstration closely, gaining a clear
understanding of the implications of using estimated parameters within test
statistics, and learning about the efficacy of the parametric bootstrap method
as a corrective measure.

@@

\section*{Data Availability Statement}
An R implementation of the proposed methods as well as teaching materials are  
included in the Supplementary Materials.

### 2024-04-29 manuscript/reply.tex
add cover, minor typo fixes to ms and reply

For blinding purposes, course numbers, author initials and websites, and 
university name have been redacted, but all this information appears in the 
unblinded version.  In brief, this material has been covered at the graduate
level in a statistical computing course, open to all graduate students in 
Statistics and others with permission, that covers the bootstrap. Detailed R 
code and graphical illustrations were provided to students in the open-access 
course notes to elucidate the distinctions between employing null
hypotheses with and without defined parameters.  This link is included in the 
unblinded version of the paper. \eds{Not sure how we can blind your github 
website for the submission unless we actually don't include it in the blinded 
version. Could we print to PDF the relevant section of the notes and include as 
a supplement for review purposes?}

Similarly at the undergraduate-level, students in an R-based applied regression 
course were provided with an R Markdown file with simulation code in order to 
demonstrate how the KS test fails with estimated parameters in the hypothesized 
distribution. The R Markdown file that was provided to students is included in 
the Supplemental Materials. This R-based applied linear regression course are 
has the following prerequisites: two semesters of introductory statistics OR a 
Calculus~2-based statistical methods course.

>>>>

For blinding purposes, course numbers, author initials and websites, and 
university name have been redacted, but all this information appears in the 
unblinded version.  In brief, this material has been covered at the graduate
level in a statistical computing course, open to all graduate students in 
Statistics and others with permission, that covers the bootstrap. Detailed R 
code and graphical illustrations were provided to students in the open-access 
course notes to elucidate the distinctions between employing null
hypotheses with and without defined parameters.  This link is included in the 
unblinded version of the paper; for the blinded review, we printed the 
relevant portion of the notes to pdf and included this blinded pdf file in the 
Supplemental Materials. %\eds{Not sure how we can blind your github 
%website for the submission unless we actually don't include it in the blinded 
%version. Could we print to PDF the relevant section of the notes and include as 
%a supplement for review purposes?}

Similarly at the undergraduate-level, students in an R-based applied regression 
course were provided with an R Markdown file with simulation code in order to 
demonstrate how the KS test fails with estimated parameters in the hypothesized 
distribution. The R Markdown file that was provided to students is included in 
the Supplemental Materials. This R-based applied linear regression course 
has the following prerequisites: two semesters of introductory statistics OR a 
Calculus~2-based statistical methods course.
